---
title: "Introduction to Uzbek Stock Market Data with *opendatauzb* package"
author: "Alisher Suyunov"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"Introduction to Uzbek Stock Market Data"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(quantmod)
library(tidyverse)
library(PerformanceAnalytics)
library(tidyquant)

asset_group <- c("UZ704532K019", "UZ7045320007", "UZ7025870005", "UZ7038380000", "UZ7025770007",
                 "UZ7015030008", "UZ7043200003", "UZ703756K015", "UZ7037560008", "UZ7016400002",
                 "UZ7004510002", "UZ7023760000", "UZ703348K011", "UZ7033480003", "UZ7035340007",
                 "UZ7028090007", "UZ701134K017", "UZ7011340005", "UZ701655K011", "UZ7016550004")

# for example it was 1
assets <- asset_group %>%
  lapply(getTicker) %>%
  bind_rows()

Ra <- assets %>%
  group_by(symbol) %>%
  tq_transmute(select     = "Closed Price",
               mutate_fun = periodReturn,
               period     = "monthly",
               col_rename = "Ra")
Ra

# Baseline
Rb <- getMarketIndex("all") %>%
  tq_transmute(select     = price,
               mutate_fun = periodReturn,
               period     = "monthly",
               col_rename = "Rb")
Rb

RaRb <- left_join(Ra, Rb, by = c("Date" = "date"))

RaRb_capm <- RaRb %>%
  tq_performance(Ra = Ra,
                 Rb = Rb,
                 Rf = 0.15,
                 performance_fun = table.CAPM)
RaRb_capm
RaRb_capm %>% select(symbol, Alpha, Beta)


RaRb %>%
  tq_performance(
    Ra = Ra,
    Rb = Rb,
    performance_fun = SharpeRatio
  )

wts <- c(rep(0.4/17, 5),
         0.15,
         rep(0.4/17, 3),
         0.20,
         rep(0.4/17, 4),
         0.25,
         rep(0.4/17, 5))

# wts <- c(rep(1/8, 8))

portfolio_growth_monthly <- Ra %>%
  tq_portfolio(assets_col   = symbol,
               returns_col  = Ra,
               weights      = wts,
               col_rename   = "investment.growth",
               wealth.index = TRUE) %>%
  mutate(investment.growth = investment.growth * 100000)

portfolio_growth_monthly %>%
  ggplot(aes(x = Date, y = investment.growth)) +
  geom_line(size = 2, color = palette_light()[[1]]) +
  labs(title = "Portfolio growth",
       subtitle = "",
       caption = "",
       x = "", y = "Portfolio Value") +
  geom_smooth(method = "loess") +
  theme_tq() +
  scale_color_tq() +
  scale_y_continuous(labels = scales::label_number())
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
