---
title: "Introduction to Uzbek Stock Market Data with *opendatauzb* package"
author: "Alisher Suyunov"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"Introduction to Uzbek Stock Market Data with *opendatauzb* package"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE, warning=FALSE}
library(rmarkdown)
library(quantmod)
library(tidyverse)
library(PerformanceAnalytics)
library(tidyquant)
library(opendatauzb)
library(knitr)
library(kableExtra)
library(formattable)
```

This vignette provides an overview of a practical use of **opendatauzb** package's functions to work with Uzbek Stock Market Data. Unlike stock markets in developed economies, there are few resources available in Uzbekistan that are machine-friendly and able to provide Uzbek stock market prices in machine-readable formats. With this R package, we overcome these data limitations and improve productivity of equity research analysts while evaluating Uzbek stocks.


# Available securities in Uzbek Stock Market

## RegisteredSecurities(): Download a full list of registered securities with ISIN and CFI codes

```opendatauzb::RegisteredSecurities()``` collects a list of securities from the [Central Securities Depository](www.deponet.uz) database.

```{r, include = TRUE, eval=FALSE, warning=FALSE}
RegisteredSecurities()
```
```{r, echo = FALSE, include = TRUE, warning=FALSE}
RegisteredSecurities() %>% head(10) %>% kable()
```

## getSecurities(): Download the securities listed on the Republican Stock Exchange "Toshkent"

```opendatauzb::getSecurities()``` provides a data frame with the list of securities from [the Republican Stock Exchange "Toshkent" database](www.uzse.uz)

```{r, include = TRUE, warning=FALSE, eval=FALSE}
getSecurities()
```
```{r, echo = FALSE, include = TRUE, warning=FALSE}
getSecurities() %>% head(10) %>% kable() %>% kable_styling()
```

## ipo(): Obtain schedule of public offerings (IPO/SPO/PO (the government shares))

```opendatauzb::ipo()``` returns a data frame with public offerings in last five years.

```{r, include = TRUE, eval = FALSE, warning = FALSE}
ipo()
```
```{r, echo = FALSE, include = TRUE, warning = FALSE}
ipo() %>% tail(10) %>% kable() %>% kable_styling()
```

## currentBidsAsks(): Watch current Bids and Asks for stocks

```opendatauzb::currentBidsAsks()``` returns current bid and ask prices on [the Republican Stock Exchange "Toshkent" database](www.uzse.uz).

```{r, include = TRUE, eval = FALSE, warning = FALSE}
currentBidsAsks()
```
```{r, echo = FALSE, include = TRUE, warning = FALSE,}
currentBidsAsks() %>% head(10) %>% select(-5) %>% kable(results = "asis") %>% kable_styling() 
```

## Market Benchmark
### getMarketIndex(): Download stock market indices over the period given across sectors

```opendatauzb::getMarketIndex()``` downloads Uzbek stock market indices (Uzbekistan Composite Index, UCI) by sectors or all sectors. The sector name should be provided as the following (case-insensitive):

 * all
 * finance
 * industry 
 * agriculture
 * construction 
 * social 
 * transport
 * trade 
 * other

```{r, include = TRUE, eval=FALSE, warning=FALSE}
getMarketIndex(sector = "all")
```
```{r, echo = FALSE, include = TRUE, warning=FALSE}
getMarketIndex(sector = "all") %>% head(10) %>% kable() %>% kable_styling()
```

The timeframe can be specified by arguments *from* and *to* provided in **"%d.%m.%Y"** date format:

```{r, include = TRUE, eval=FALSE, warning=FALSE}
getMarketIndex(sector = "finance",
               from = "01.01.2018",
               to = "30.06.2020")
```
```{r, echo = FALSE, include = TRUE, warning=FALSE}
getMarketIndex(sector = "finance",
               from = "01.01.2018",
               to = "30.06.2020") %>% head(10) %>% kable() %>% kable_styling()
```

## getTicker(): Load stock market prices for certain timeframe

```opendatauzb::getTicker()``` obtains stock market prices by security code over the period given:

```{r, include = TRUE, eval=FALSE, warning=FALSE}
getTicker("UZ7011340005")
```
```{r, echo = FALSE, include = TRUE, warning=FALSE}
getTicker("UZ7011340005") %>% head(10) %>% select(-9, -10) %>% kable() %>% kable_styling()
```

```{r, include = TRUE, eval=FALSE, warning=FALSE}
getTicker("UZ7011340005", 
          from = "01.01.2018", 
          to = "30.06.2020")
```
```{r, echo = FALSE, include = TRUE, warning=FALSE, message = FALSE}
getTicker("UZ7011340005", 
          from = "01.01.2018", 
          to = "30.06.2020") %>% head(10) %>% select(-9, -10) %>% kable() %>% kable_styling()
```



# Constructing a portfolio with Uzbek Stocks

## Creating a data frame with stock prices

For this example, we use **opendatauzb** package's functions and other packages (```quantmod```, ```PerformanceAnalytics```, ```tidyquant```) for financial modelling to evaluate the given set of stocks and portfolio performance. we have chosen 20 stocks, including **Kvarts, Trustbank, Hamkorbank, UzSQB, ToshkentVino** and others.

Using ```getTicker``` function, we download stock prices for each of those stocks. **Note**: if arguments *from* and *to* are not provided, by default, both ```getMarketIndex()``` and ```getTicker()``` functions download stock prices starting from 01.01.2019.

```{r, include = TRUE, warning=FALSE, message=FALSE}
asset_group <- c("UZ704532K019", "UZ7045320007", "UZ7025870005", "UZ7038380000", "UZ7025770007",
                 "UZ7015030008", "UZ7043200003", "UZ703756K015", "UZ7037560008", "UZ7016400002",
                 "UZ7004510002", "UZ7023760000", "UZ703348K011", "UZ7033480003", "UZ7035340007",
                 "UZ7028090007", "UZ701134K017", "UZ7011340005", "UZ701655K011", "UZ7016550004")

assets <- asset_group %>%
  lapply(getTicker) %>%
  bind_rows()
```

Having loaded stock prices, we calculate monthly returns using a ```tidyquant::tq_transmute()``` function from ```tidyquant``` package. Please refer to the [link](https://cran.r-project.org/web/packages/tidyquant/vignettes/TQ05-performance-analysis-with-tidyquant.html) for more information on using ```tidyquant``` package.

As Uzbek Stock Market databases do not provide adjusted closing prices, for this example, we use closing prices. However, in real-world practice, we highly recommend calculating [adjusted closing prices](https://finance.zacks.com/adjusted-closing-price-vs-closing-price-9991.html). 

```{r, include = TRUE, warning=FALSE}
Ra <- assets %>%
  group_by(symbol) %>%
  tq_transmute(select     = "Closed Price",
               mutate_fun = periodReturn,
               period     = "monthly",
               col_rename = "Ra")
```

The output presents only first six rows of calculated monthly returns.

```{r, echo = FALSE, include = TRUE, warning=FALSE}
kable(head(Ra, n = 6)) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

## Market Index (Uzbekistan Composite Index, UCI)

After collecting data for our stocks, we download overall market index as baseline prices for our analysis.

```{r, echo=TRUE, warning=FALSE}
# Baseline prices
Rb <- getMarketIndex("all") %>%
  tq_transmute(select     = price,
               mutate_fun = periodReturn,
               period     = "monthly",
               col_rename = "Rb")
```

```{r, echo = FALSE, include = TRUE, warning=FALSE}
Rb %>% head(6) %>% kable() %>% kable_styling()
RaRb <- left_join(Ra, Rb, by = c("Date" = "date"))
```

## Building the Capital Asset Pricing Model (CAPM)

To evaluate if the stock is valued fairly considering associated risks and expected returns, we employ [CAPM](https://corporatefinanceinstitute.com/resources/knowledge/finance/what-is-capm-formula/) model. We use ```tidyquant::tq_performance()``` function from ```tidyquant``` package.

```{r, echo=TRUE, warning=FALSE, message=FALSE}
RaRb_capm <- RaRb %>%
  tq_performance(Ra = Ra,
                 Rb = Rb,
                 Rf = 0.15,
                 performance_fun = table.CAPM)
```

```{r, echo = FALSE, include = TRUE, warning=FALSE}
RaRb_capm %>% 
  select(1:3,5, 10, 12, 13) %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

## Calculating Sharpe ratio for individual stocks 

We estimate Sharpe ratio for all our stocks to see returns on investment per amount of taken risks. As a rule of thumb, the Sharpe ratio greater than 3 is classified as **Excellent**, an interval 2.00-2.99 is **Very Good**, 1.00-1.99 range is **Acceptable**, the ratio less than 1 is classified as **Bad or Sub-optimal**.

```{r, echo=TRUE, warning=FALSE, message=FALSE}
RaRb %>%
  tq_performance(Ra = Ra,
    Rb = NULL,
    performance_fun = SharpeRatio,
    Rf = 0.15) %>% 
  formattable(list("ESSharpe(Rf=15%,p=95%)" = formatter("span", 
                                                        style = x ~ ifelse(x >= 3, 
                                                                           style(color = "green", 
                                                                                 font.weight = "bold"), 
                                                                           NA))))
```


## (Single) Portfolio performance

Based on the ratios we calculated above, we choose two stocks for our portfolio: **UZ7015030008 (MSBU)** and **UZ7035340007 (UZKB)**.

```{r , warning=FALSE, message=FALSE}
wts <- c(rep(0, 5),
         0.35, #6
         rep(0, 8),
         0.65, #15
         rep(0, 5))

portfolio_returns_monthly <- Ra %>%
  tq_portfolio(assets_col   = symbol,
               returns_col  = Ra,
               weights      = wts,
               col_rename   = "Ra")

left_join(portfolio_returns_monthly, 
          Rb,
          by = c("Date"="date")) %>% 
  tq_performance(Ra = Ra, Rb = Rb, performance_fun = table.CAPM) %>% 
  gather() %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

## Portfolio growth

On condition that our initial assumptions hold, let us see how 100,000 UZS investment in these stocks would grow since 1 January 2019. 

```{r , warning=FALSE, message=FALSE}
portfolio_growth_monthly <- Ra %>%
  tq_portfolio(assets_col   = symbol,
               returns_col  = Ra,
               weights      = wts,
               col_rename   = "investment.growth",
               wealth.index = TRUE) %>%
  mutate(investment.growth = investment.growth * 100000)
```

As the graph below shows, the initial investment of 100,000 UZS in these 2 stocks in 1 January 2019 is worth around 2.2M UZS as of 30 June 2020 without inflation adjustment.

**Note:** These estimates are for only illustrative purposes of the practical use of *opendatauzb* package. The real returns on investment may rely heavily on the assumptions drawn earlier and other exogenous shocks to Uzbek Stock Market.


```{r echo=FALSE, fig.height=5, fig.width=7, message=FALSE, , warning=FALSE}
portfolio_growth_monthly %>%
  ggplot(aes(x = Date, y = investment.growth)) +
  geom_line(size = 2, color = palette_light()[[1]]) +
  labs(title = "Portfolio growth",
       subtitle = "35% MSBU and 65% UZKB",
       caption = "",
       x = "", y = "Portfolio Value (thousand UZS)") +
  geom_smooth(method = "loess") +
  theme_tq() +
  scale_color_tq() +
  scale_y_continuous(labels = scales::unit_format(unit = "", scale = 1e-3))
```
